Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-01 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Edit so bullet points will format
move lables so an see dade plot more clealry

Good Characteristics:
- Flooding-- Most associated with death; property damage
- Precipitation
- Wind (potentially weighted)

Bad Characteristics:
- Distance alone
- Wind alone

>>>>

Good Characteristics:
- Measureable at the county/sub-county level
- Internally consistant (either within a study or for a particular storm)
+ Takes into account the unique characteristics of a particular storm and county's location in assessing exposure
- Flooding-- Most associated with death; property damage
- Precipitation
- Wind (potentially weighted)

Bad Characteristics:
- Distance alone
- Wind alone
- Metrics that cannot be widely measured at the county or sub-county level (i.e., stress)
